---
title: "Self-Reliance Plan"
params:
  set_author: placeholder
  set_date: placeholder
  set_member: placeholder
  set_spouse: placeholder
  set_needs: placeholder
  set_income: placeholder
  set_expenses: placeholder
  set_financeBalance: placeholder
  set_financePlot: placeholder
  set_resourcesIndividual: resourcesIndividual
  set_resourcesFamily: resourcesFamily
  set_resourcesCommunity: resourcesCommunity
  set_myPlan: myPlan
  set_serviceIdeas: NA
  set_servicePlan: NA
author: "`r params$set_author`"
date: "`r params$set_date`"
output: html_document
---
### Needs
*Immediate needs may include food, clothing, medical or emotional care, or housing. Longer-term needs may include education or improved employment.*
```{r needs, echo=FALSE}
tags$p(tags$strong(params$set_needs))
```

### Income and Expenses

#### Income
```{r income, echo=FALSE}
params$set_income
```

#### Expenses
```{r expenses, echo=FALSE}
params$set_expenses
```

#### Budget Summary
<blockquote>
```{r financeBalance, echo=FALSE}
tags$span(params$set_financeBalance)
```
</blockquote>

```{r financePlot, echo=FALSE, fig.width = 10, fig.height = 7}
params$set_financePlot
```

### Available Resources
<p>
<u>Individual resources and skills</u>: 
```{r resInd, echo=FALSE}
tags$span(tags$strong(params$set_resourcesIndividual))
```
</p>
<p>
<u>Help and resources available from family members (parents, children, siblings, others)</u>:
```{r resFam, echo=FALSE}
tags$span(tags$strong(params$set_resourcesFamily))
```
</p>
<p>
<u>Relevant community resources</u>:
```{r resCom, echo=FALSE}
tags$span(tags$strong(params$set_resourcesCommunity))
```
</p>

### My Plan to Become More Self-Reliant
```{r myPlan, echo=FALSE}
params$set_myPlan
```

### Work or Service
My work or service contribution in return for any assistance I may receive  
<u>Ideas to share with the bishop or branch president</u>:
```{r serviceIdeas, echo=FALSE}
tags$strong(params$set_serviceIdeas)
```

<u>The work or service assignment agreed to with the bishop or branch president</u>:
```{r servicePlan, echo=FALSE}
tags$strong(params$set_servicePlan)
```

### My Commitment
This was digitally signed by: <strong>`r params$set_member`</strong> on <strong>`r params$set_date`</strong>.
Spouse digital signature: <strong>`r params$set_spouse`</strong> on <strong>`r params$set_date`</strong>.