---
title: "Self-Reliance Plan"
params:
  set_author: placeholder
  set_date: placeholder
  set_member: placeholder
  set_spouse: placeholder
  set_needs: placeholder
  set_income: placeholder
  set_expenses: placeholder
  set_financeBalance: placeholder
  set_financePlot: placeholder
  set_resourcesIndividual: resourcesIndividual
  set_resourcesFamily: resourcesFamily
  set_resourcesCommunity: resourcesCommunity
  set_myPlan: myPlan
  set_serviceIdeas: NA
  set_servicePlan: NA
author: "`r params$set_author`"
date: "`r params$set_date`"
output: html_document
---
### Step 1: What are my needs?
<div class="bg bg-info">
Immediate needs may include food, clothing, medical or emotional care, or housing. Longer-term needs may include education or improved employment.
</div>
```{r needs, echo=FALSE}
tags$p(params$set_needs)
```

### Step 2: What are my income and expenses?

#### Monthly income
```{r income, echo=FALSE}
params$set_income
```

#### Monthly expenses
```{r expenses, echo=FALSE}
params$set_expenses
```

#### Budget Summary
##### Plain-text interpretation of budget:
```{r financeBalance, echo=FALSE}
tags$cite(params$set_financeBalance)
```


```{r financePlot, echo=FALSE, fig.width = 10, fig.height = 7}
params$set_financePlot
```

### Step 3: What other resources are available?
<ul><li><span class = "bg bg-info">Individual resources and skills:</span> 
```{r resInd, echo=FALSE}
tags$span(params$set_resourcesIndividual)
```
<li><span class = "bg bg-info">Help and resources available from family members (parents, children, siblings, others):</span> 
```{r resFam, echo=FALSE}
tags$span(params$set_resourcesFamily)
```
<li><span class = "bg bg-info">Relevant community resources:</span> 
```{r resCom, echo=FALSE}
tags$span(params$set_resourcesCommunity)
```
</ul>

### Step 4: What is my personal or family plan to become more self-reliant?
<p class="bg bg-info">As part of your plan, consider participating in a self-reliance group.</p>
```{r myPlan, echo=FALSE}
params$set_myPlan
```

### Step 5: What work or service will I contribute in return for any assistance I may receive?
<ul>
<li><span class="bg bg-info">Ideas to share with the bishop or branch president:</span> 
```{r serviceIdeas, echo=FALSE}
tags$span(params$set_serviceIdeas)
```

<span class="bg bg-info">After consulting with the bishop or branch president, describe the work or service assignment you will do:</span> 
```{r servicePlan, echo=FALSE}
tags$span(params$set_servicePlan)
```
</ul>

### Commitment
`r if(shiny::isTruthy(params$set_member)){"<span class='bg bg-info'>Member's signature:</span> "}`
<span>`r params$set_member`</span> <cite>`r if(shiny::isTruthy(params$set_member)){params$set_date}`</cite>

`r if(shiny::isTruthy(params$set_spouse)){"<span class='bg bg-info'>Spouse's signature:</span> "}`
<span>`r params$set_spouse`</span> <cite>`r if(shiny::isTruthy(params$set_spouse)){params$set_date}`</cite>